Unbiased pangenome graphs

### 2022-10-08 manuscript/main.tex
tweak the redundant sentence

The set of alignments represented by a variation graph may be strictly larger than the set of alignments used to induce it.
The graph must contain at least the set of alignments given in input.
It may also contain new implied pairwise relationships that arise due to transitive match relationships, as shown in Figure \ref{fig:induction} for closures 1 and 6.
However, by definition of $\mathcal{G}$, it cannot contain \textit{less} match information than represented in the set of matches ($A$).

>>>>

The set of alignments represented by a variation graph may be strictly larger than the set of alignments used to induce it.
The graph must contain at least the set of alignments given in input.
In other words, by definition of $\mathcal{G}$, it cannot contain \textit{less} match information than represented in the set of matches ($A$).
However, the graph may also contain new implied pairwise relationships that arise due to transitive match relationships, as shown in Figure \ref{fig:induction} for closures 1 and 6.
